Quantifying uncertainty in Pareto estimates of global lake area

### 2023-01-30 manuscript/manuscript.tex
prep for accepted release

% Uncomment to override  the `A preprint' in the header
%\renewcommand{\headeright}{Technical Report}
%\renewcommand{\undertitle}{Technical Report}
\renewcommand{\shorttitle}{Pareto lake area uncertainty}

@@

>>>>

% Uncomment to override  the `A preprint' in the header
\renewcommand{\headeright}{\href{https://doi.org/}{DOI: 10.XXX/XXX}}
\renewcommand{\undertitle}{This is an Accepted Manuscript of an article published in Limnology \& Oceanography: Methods \href{https://doi.org/}{DOI: 10.XXX/XXX}}
\renewcommand{\shorttitle}{Pareto lake area uncertainty}

@@

\section{Data Availability Statement}

All data and code associated with this manuscript are available at: \href{https://doi.org/10.5281/zenodo.7459226}{https://doi.org/10.5281/zenodo.7459226}

\section{Acknowledgements}

This work was supported by the U.S. National Science Foundation’s Harnessing the Data Revolution Program (OAC-1934633) and Los Alamos National Laboratory (LDRD-20210213ER, LDRD-20220697PRD1). I thank the following individuals for a friendly review of an earlier draft: P.C. Hanson, E. Zipkin.
